---
title: "R Notebook"
output: html_notebook
---


Change the abreviations



Library 
```{r}
library(ggplot2)
library(dplyr)
library(corrplot)
library(ggpubr)
library(gridExtra)
```

Read in Docs
```{r}
Bmore <- read.csv("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\GitHub\\nrastegthesis\\R2_Recalculate.csv")
Mon2020 <- read.csv("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\GitHub\\nrastegthesis\\Monitor_2020.csv")
MonWebs <- read.csv("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\GitHub\\nrastegthesis\\Air_Mon_Recalculate.csv")
AADT <- read.csv("C:/Users/Nava/OneDrive/Documents/Desktop/GitHub/nrastegthesis/AADT_INF_STA.csv")
```

Summary

```{r}
Mon2020S <- Mon2020 %>% group_by(Site)
Monsump <- Mon2020S %>% summarise(
  Alper = mean(Al., na.rm= TRUE),
  Alpersd = sd(Al., na.rm= TRUE),
  Feper = mean(Fe., na.rm=TRUE),
  Fepersd = sd(Fe., na.rm= TRUE),
  Pbper = mean(Pb., na.rm=TRUE),
  Pbpersd = sd(Pb., na.rm= TRUE)
)
Monsump$Site <- gsub("HU", "HU Beltsville", Monsump$Site)
Monsump$Site <- gsub("ES", "Essex", Monsump$Site)


Mon2020S <- Mon2020 %>% group_by(Site)
Monsums <- Mon2020S %>% summarise(
  Almean = mean(Al, na.rm= TRUE),
  Alsd = sd(Al, na.rm= TRUE),
  Femean = mean(Fe, na.rm=TRUE),
  Fesd = sd(Fe, na.rm= TRUE),
  Pbmean = mean(Pb, na.rm=TRUE),
  Pbsd = sd(Pb, na.rm= TRUE),
  PMmean= mean(PM, na.rm=TRUE),
  PMsd = sd(PM, na.rm=TRUE)
)

Monsums$Site <- gsub("HU", "HU Beltsville", Monsums$Site)
Monsums$Site <- gsub("ES", "Essex", Monsums$Site)

MonwebS <- MonWebs %>% group_by(Area)
Websum <- MonwebS %>% summarise(
  Alper = mean(Al_perc_day, na.rm= TRUE),
  Alpersd = sd(Al_perc_day, na.rm= TRUE),
  Feper = mean(Fe_Perc_Day, na.rm=TRUE),
  Fepersd = sd(Fe_Perc_Day, na.rm= TRUE),
  Pbper = mean(Pb_Perc_Day, na.rm=TRUE),
  Pbpersd = sd(Pb_Perc_Day, na.rm= TRUE)
)

Websum$Area <- gsub("HU", "HU Beltsville", Websum$Area)
Websum$Area <- gsub("ES", "Essex", Websum$Area)

```


```{r}
BmoreG<- Bmore %>% group_by(Neighborhood)
BmoreSum <- BmoreG %>% summarise(
  Alper = mean(Al_per_day, na.rm= TRUE),
  Alpersd = sd(Al_per_day, na.rm= TRUE),
  Feper = mean(Fe_per_day, na.rm=TRUE),
  Fepersd = sd(Fe_per_day, na.rm= TRUE),
  Pbper = mean(Pb_per_day, na.rm=TRUE),
  Pbpersd = sd(Pb_per_day, na.rm= TRUE)
)

BmoreSum$Neighborhood <- gsub("BK", "Brooklyn", BmoreSum$Neighborhood)
BmoreSum$Neighborhood <- gsub("CB", "Curtis Bay", BmoreSum$Neighborhood)
```

Plot of baltimore values 
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\bmorewebsfe.jpg", width = 1000, height = 600)
# 2. Create the plot
# First row with scatter plot
ggplot(BmoreSum, aes(x=Neighborhood, y=Feper)) +
    geom_bar( aes(x=Neighborhood, y=Feper), stat="identity", fill="firebrick", alpha=1) +
  geom_linerange( aes(x=Neighborhood, ymin=Feper- Fepersd, ymax=Feper + Fepersd), colour="springgreen3", alpha=1, size=1.3)+
    xlab("") +
            geom_text(aes(label="*"), position = position_nudge(.05), vjust = -.05, size=15)+
  ylab ("% Fe in webs per day") +
     theme(panel.background = element_rect(fill = 'white', colour = 'gray')) + 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\bmorewebsal.jpg", width = 1000, height = 600)
# 2. Create the plot
# First row with scatter plot
 ggplot(BmoreSum, aes(x=Neighborhood, y=Alper)) +
    geom_bar( aes(x=Neighborhood, y=Alper), stat="identity", fill="deepskyblue", alpha=1) +
  geom_linerange( aes(x=Neighborhood, ymin=Alper- Alpersd, ymax=Alper + Alpersd), colour="orange", alpha=1, size=1.3) +
    xlab("") +
  ylab ("% Al in webs per day") +
     theme(panel.background = element_rect(fill = 'white', colour = 'gray')) + 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\bmorewebsal.jpg", width = 1000, height = 600)
# 2. Create the plot
# First row with scatter plot
 ggplot(BmoreSum, aes(x=Neighborhood, y=Alper)) +
    geom_bar( aes(x=Neighborhood, y=Alper), stat="identity", fill="deepskyblue", alpha=1) +
  geom_linerange( aes(x=Neighborhood, ymin=Alper- Alpersd, ymax=Alper + Alpersd), colour="orange", alpha=1, size=1.3) +
    xlab("") +
  ylab ("% Al in webs per day") +
     theme(panel.background = element_rect(fill = 'white', colour = 'gray')) + 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()

```

Plot of PM values 
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\monPM.jpg", width = 1000, height = 600)
ggplot(MonsumPM) +
  geom_bar( aes(x=Site, y=PMmean), stat="identity", fill="gold2", alpha=1) +
  geom_linerange( aes(x=Site, ymin=PMmean-PMsd, ymax=PMmean+PMsd), colour="black", alpha=1, size=1.3)+
  theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  xlab("") + ylab("PM 2.5 (µg/m3)")+
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```
Plot of monitor percents
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\monPb.jpg", width = 1000, height = 600)
 ggplot(Monsump) +
  geom_bar( aes(x=Site, y=Pbper), stat="identity", fill="darkorchid", alpha=1) +
  geom_linerange( aes(x=Site, ymin=Pbper- Pbpersd, ymax=Pbper+Pbpersd), colour="deeppink", alpha=1, size=1.3)+
  xlab("") +
  ylab ("% Pb in PM 2.5") +
  theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\monAl.jpg", width = 1000, height = 600)
ggplot(Monsump) +
  geom_bar( aes(x=Site, y=Alper), stat="identity", fill="deepskyblue", alpha=1) +
  geom_linerange( aes(x=Site, ymin=Alper- Alpersd, ymax=Alper+Alpersd), colour="orange", alpha=1, size=1.3)+
  xlab("") +
  ylab ("% Al in PM 2.5") +
     theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```

```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\monFe.jpg", width = 1000, height = 600)
ggplot(Monsump, aes(x=Site, y=Feper)) +
  geom_bar( aes(x=Site, y=Feper), stat="identity", fill="firebrick", alpha=1) +
  geom_linerange( aes(x=Site, ymin=Feper- Fepersd, ymax=Feper+Fepersd), colour="springgreen3", alpha=1, size=1.3) +
  xlab("") +
  ylab ("% Fe in PM 2.5") +
       geom_text(aes(label="*"), position = position_nudge(.05), vjust = -.05, size=15)+
     theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```

```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\monFe.jpg", width = 1000, height = 600)
ggplot(Monsump, aes(x=Site, y=Feper)) +
  geom_bar( aes(x=Site, y=Feper), stat="identity", fill="firebrick", alpha=1) +
  geom_linerange( aes(x=Site, ymin=Feper- Fepersd, ymax=Feper+Fepersd), colour="springgreen3", alpha=1, size=1.3) +
  xlab("") +
  ylab ("% Fe in PM 2.5") +
       geom_text(aes(label="*"), position = position_nudge(.05), vjust = -.05, size=15)+
     theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```

Plot of web values
```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\WebAl.jpg", width = 1000, height = 600)
ggplot(Websum, aes(x=Area, y=Alper)) +
  geom_bar( aes(x=Area, y=Alper), stat="identity", fill="deepskyblue", alpha=1) +
  geom_linerange( aes(x=Area, ymin=Alper- Alpersd, ymax=Alper+Alpersd), colour="orange", alpha=1, size=1.3) +
  xlab("") +
  ylab ("% Al in webs by day") +
   geom_text(aes(label="*"), position = position_nudge(.05), vjust = -.05, size=15)+
     theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
dev.off()
```

```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\WebFe.jpg", width = 1000, height = 600)

 ggplot(Websum) +
  geom_bar( aes(x=Area, y=Feper), stat="identity", fill="firebrick", alpha=1) +
  geom_linerange( aes(x=Area, ymin=Feper- Fepersd, ymax=Feper+Fepersd), colour="springgreen3", alpha=1, size=1.3) +
  xlab("") +
  ylab ("% Fe in webs by day") +
     theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
 dev.off()

```

```{r}
jpeg("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\FIEE paper\\WebPb.jpg", width = 1000, height = 600)
ggplot(Websum, aes(x=Area, y=Pbper)) +
  geom_bar( aes(x=Area, y=Pbper), stat="identity", fill="darkorchid", alpha=1) +
  geom_linerange( aes(x=Area, ymin=Pbper- Pbpersd, ymax=Pbper+Pbpersd), colour="deeppink", alpha=1, size=1.3) +
  xlab("") +
  ylab ("% Pb in webs by day") +
  geom_text(aes(label="*"), position = position_nudge(.05), vjust = -.05, size=15)+
  theme(panel.background = element_rect(fill = 'white', colour = 'gray'))+ 
  theme(text=element_text(size=24,  family="TT Arial"))
 dev.off()

```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
