---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---


```{r}
library(dplyr)
library(EnvStats)
library(devtools)
library(githubinstall)
library(agricolae)
library(gtools)
```

```{r}
MonWebs <- read.csv("C:\\Users\\student\\Downloads\\FIEE paper\\FIEE paper\\monitor_webs.csv")

Bmore <- read.csv("C:\\Users\\student\\Downloads\\FIEE paper\\FIEE paper\\bmore_webs.csv")

MonWebs0 <- read.csv("C:\\Users\\student\\Downloads\\FIEE paper\\FIEE paper\\air_mon_0.csv")

Bmore0 <- read.csv("C:\\Users\\student\\Downloads\\FIEE paper\\FIEE paper\\bmore_0.csv")

Mon2020 <- read.csv("C:\\Users\\student\\Downloads\\FIEE paper\\FIEE paper\\FRM_HUES.csv")

R1_R2 <- read.csv("C:\\Users\\student\\Downloads\\FIEE paper\\FIEE paper\\R2_R1.csv")

full_bmore <- read.csv("C:\\Users\\Nava\\OneDrive\\Documents\\Desktop\\GitHub\\nrastegthesis\\full_bmore")

```

```{r}
BmoreLog <- Bmore
BmoreLog$Al_per_day <- logit(BmoreLog$Al_per_day/100)
BmoreLog$Fe_per_day <- logit(BmoreLog$Fe_per_day/100)
BmoreLog$Pb_per_day <- logit(BmoreLog$Pb_per_day/100)

Bmore0Log <- Bmore0
Bmore0Log$Al_per_day <- logit(Bmore0Log$Al_per_day/100)
Bmore0Log$Fe_per_day <- logit(Bmore0Log$Fe_per_day/100)
Bmore0Log$Pb_per_day <- logit(Bmore0Log$Pb_per_day/100)

MonwebLog <- MonWebs
MonwebLog$Al_perc_day <- logit(MonwebLog$Al_perc_day/100)
MonwebLog$Fe_Perc_Day <- logit(MonwebLog$Fe_Perc_Day/100)
MonwebLog$Pb_Perc_Day <- logit(MonwebLog$Pb_Perc_Day/100)

MonwebLog0 <- MonWebs0
MonwebLog0$Al_perc_day <- logit(MonwebLog0$Al_perc_day/100)
MonwebLog0$Fe_Perc_Day <- logit(MonwebLog0$Fe_Perc_Day/100)
MonwebLog0$Pb_Perc_Day <- logit(MonwebLog0$Pb_Perc_Day/100)

```


Monitor PM significance

Not Sig
```{r}
t.test(Mon2020$PM ~ Mon2020$Site, method="spearmans")
```


```{r}
hist(Mon2020$PM)
```

Al RAW Not sig
```{r}
t.test(Mon2020$Al ~ Mon2020$Site, method="spearmans")
```

```{r}
hist(Mon2020$Al)
```
Al % Not sig
```{r}
t.test(Mon2020$Al. ~ Mon2020$Site, method="spearmans")
```

```{r}
hist(Mon2020$Al.)
```
Pb RAW not sig
```{r}
t.test(Mon2020$Pb ~ Mon2020$Site, method="spearmans")
```

```{r}
hist(Mon2020$Pb)
```

Pb % not sig
```{r}
t.test(Mon2020$Pb. ~ Mon2020$Site, method="spearmans")
```

```{r}
hist(Mon2020$Pb.)
```
Fe Not sig
```{r}
t.test(Mon2020$Fe ~ Mon2020$Site, method="spearmans")
```

```{r}
hist(Mon2020$Fe)
```
Fe percent- sig, HU higher 
```{r}
t.test(Mon2020$Fe. ~ Mon2020$Site, method="spearmans")
```

```{r}
hist(Mon2020$Fe.)
```

Web Monitor UNTRANSFORMED 
Al- sig
ES higher

```{r}
t.test(MonWebs$Al_perc_day~ MonWebs$Area, method="spearman" )
```

```{r}
hist(MonWebs$Al_perc_day)
```

Pb- sig
ES Higher 
```{r}
t.test(MonWebs$Pb_Perc_Day~ MonWebs$Area, method="spearman" )
```
```{r}
hist(MonWebs$Pb_Perc_Day)
```

Fe Not sig
HU higher
```{r}
t.test(MonWebs$Fe_Perc_Day~ MonWebs$Area, method="spearman" )

```

```{r}
hist(MonWebs$Fe_Perc_Day)
```

Baltimore webs percent untransformed

Al- not sig
```{r}
t.test(Bmore$Al_per_day~ Bmore$Neighborhood, method="spearman" )
```

```{r}
hist(Bmore$Al_per_day)
```
Fe- Sig
```{r}
t.test(Bmore$Fe_per_day~ Bmore$Neighborhood, method="spearman" )
```

```{r}
hist(Bmore$Fe_per_day)
```
Pb- not Sig
```{r}
t.test(Bmore$Pb_per_day~ Bmore$Neighborhood, method="spearman" )
```

```{r}
hist(Bmore$Pb_per_day)
```

UNTRANSFORMED WITH 0s
Bmore

Fe- Sig, BK larger
```{r}
t.test(Bmore0$Fe_per_day~ Bmore0$Neighborhood, method="spearman" )
```
Pb- not sig, BK higher
```{r}
t.test(Bmore0$Pb_per_day~ Bmore0$Neighborhood, method="spearman" )
```
Al- not sig, Bk larger
```{r}
t.test(Bmore0$Al_per_day~ Bmore0$Neighborhood, method="spearman" )
```



R2_R1 comparison


```{r}
t.test(R1_R2$Pb_Percent, R1_R2$PbPerc, method="spearmans")
```
Fe sig
```{r}
t.test(R1_R2$Fe_Percent, R1_R2$FePerc, method="spearmans")
```
Pb not sig 
```{r}
t.test(R1_R2$Al_Percent, R1_R2$AlPerc, method="spearmans")
```
Sig, x higher 
```{r}
t.test(R1_R2$Weight, R1_R2$Weight.mL, method="spearmans")
```
AADT COMP
no significant difference in aadt mean
```{r}
t.test(full_bmore$AADT_mean~full_bmore$Neighborhood, method="spearmans")
```

```{r}
t.test(full_bmore$AADT_max~full_bmore$Neighborhood, method="spearmans")
```

